Uncovering underlying high-level musical content in the temporal domain \\ \small Leveraging deep learning, inductive bias, and aural music skills to learn embedding spaces from raw waveforms with applications to MIR downstream tasks

### 2023-05-09 introduction/Subsections/Assumptions.tex
Updates from Overleaf

>>>>

\begin{figure}
    \scalebox{0.9}{
    \centering
    \includegraphics[width=\textwidth]{figures/images/Mahler 9 Giant Steps score.png}
        }
    \caption[]{\small{A small yet evocative excerpt from Mahler's 9th Symphony, 2nd movement: The melodic contour weaves and leaps while the harmony propels through non-diatonic major thirds, painting a vivid and almost atonal canvas.}}
    \label{fig:mahler}
\end{figure}

\begin{figure}
    \scalebox{0.9}{
    \centering
    \includegraphics[width=\textwidth]{figures/images/giant steps score.png}
        }
    \caption[]{\small{John Coltrane's Giant Steps head: A testament to harmonic exploration, featuring rapid chord changes in thirds, pushing the boundaries of jazz improvisation and technique.}}
    \label{fig:giant_steps}
\end{figure}

\begin{figure}
    \scalebox{0.9}{
    \centering
    \includegraphics[width=\textwidth]{figures/images/train interlude score.png}
        }
    \caption[]{\small{Pat Metheny's Last Train Home interlude: A masterful fusion of intricate guitar work, showcasing rhythmic precision and melodic nuance, that transports listeners through a tapestry of sonic landscapes.}}
    \label{fig:last_train}
\end{figure}
